Texture Mapping 3D Models of Indoor Environments with Noisy Camera Poses

### 2014-01-04 spie2014/spie2014.tex
minimal, just runtime now

  \caption{Texture alignment via (a) the graph-based localization
    refinement algorithm, (b) the AutoStitch software package, and (c)
    the proposed method.}
  \label{fig:mosaic3D}
\end{figure}

@@

\begin{figure}
  \centering
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_v.png}
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_2d.png}
  \includegraphics[width=2.2in,height=1.5in]{results_swarm_3_3d.png}\\
  \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_v.png}
  } \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_2d.png}
  } \subfloat[][]{
    \includegraphics[width=2.1in,height=2in]{results_swarm_5_3d.png}
  }
  \caption{The same indoor environments, as generated using (a) PCA
    plane-fitting, (b) Floor plan extrusion, (c) Voxel carving. The
    first two are lower-resolution models, while the third is
    higher-resolution, and reconstructs significantly more features,
    such as the ladder in the lower image.}
  \label{fig:modelcomparisons}
\end{figure}
\begin{figure}
  \includegraphics[width=3.1in]{results_houston_2_2d.png}
  \includegraphics[width=3.1in]{results_houston_2_3d.png}\\
  \subfloat[][]{
    \includegraphics[width=3.1in]{results_houston_3_2d.png}
  } \subfloat[][]{
    \includegraphics[width=3.1in]{results_houston_3_3d.png}
  }
  \caption{(a) A model generated by the low-resolution floor plan
    method. (b) A model generated by the high-resolution voxel-carving
    method. The high-resolution model contains far more surface
    detail, such as in the ceiling indentations or the benches on the
    ground. In terms of producing a realistic visualization however,
    the low-resolution model performs very similarly to the
    high-resolution model.}
  \label{fig:2dvs3d}
\end{figure}

The texture mapping procedure in this paper was tested with three
different geometry-reconstruction methods, a PCA-based plane-fitting
method \cite{sanchez2012point}, a floor plan extrusion method
\cite{turnerfloorplan}, and a voxel-carving mesh generation method
\cite{turnerwatertight}. The first two methods generate very similar
low-resolution models, containing only major walls, ceilings and
floors. The third method generates high-resolution models, and
attempts to reconstruct all scanned objects in the environment. A
comparison of the three model types is in Figure
\ref{fig:modelcomparisons}, while Figure \ref{fig:2dvs3d} compares the
latter 2 types for a closer comparison of a low-resolution model vs a
high-resolution model.

>>>>

  \caption{Texture alignment via (a) the graph-based localization
    refinement algorithm, (b) the AutoStitch software package, and (c)
    the method proposed in this paper.}
  \label{fig:mosaic3D}
\end{figure}

@@

\begin{figure}
  \centering{
    \includegraphics[width=3in]{threestoryfull2.png}
    \includegraphics[width=3in]{threestoryfull.png} \\
    \includegraphics[width=3in]{fullmodel.png}
    \includegraphics[width=3in]{pier15.png}
  }
  \caption{Textured models from the PCA-based approach.}
  \label{fig:pcaModels}
\end{figure}

\begin{figure}
  \centering{
    \includegraphics[width=3in]{houston2d1.png}
    \includegraphics[width=3in]{coryf2.jpg} \\
    \includegraphics[width=3in]{houston3_2.png}
    \includegraphics[width=3in]{office.png}
  }
  \caption{Textured models from the floor plan extrusion approach.}
  \label{fig:fpModels}
\end{figure}

\begin{figure}
  \centering{
    \includegraphics[width=3in]{houston2.jpg}
    \includegraphics[width=3in]{results_houston_1_3d.png} \\
    \includegraphics[width=3in]{bhh3d2.png}
    \includegraphics[width=3in]{bhh3d3.png}
  }
  \caption{Textured models from the voxel-carving approach.}
  \label{fig:voxelModels}
\end{figure}

The texture mapping procedure in this paper was tested with three
different geometry-reconstruction methods, a PCA-based plane-fitting
method \cite{sanchez2012point}, a floor plan extrusion method
\cite{turnerfloorplan}, and a voxel-carving mesh generation method
\cite{turnerwatertight}. The first two methods generate very similar
low-resolution models, containing only major walls, ceilings and
floors. The third method generates high-resolution models, and
attempts to reconstruct all scanned objects in the
environment. Texture mapped models generated by the PCA-based, floor
plan extrusion, and voxel-carving approaches, can be seen in Figures
\ref{fig:pcaModels}, \ref{fig:fpModels}, and \ref{fig:voxelModels}
respectively.
